### 2020-03-28 LaTeX_2020_Template_Full-Paper/LaTeX_2020_Template_Full Paper/main.tex
Initial Overleaf Import

\documentclass{scsSimAUDPaperFormat}
% Beginning of preable.
% Ensure that the copyright notice matches the conference/symposium.
\copyrightnotice{
	SimAUD 2020 May 25-27 Vienna, Austria

	\copyright\,2020 Society for Modeling \& Simulation International (SCS)
}
% Load basic packages
\usepackage{balance}		% to better equalize the last page
\usepackage{graphics}		% for EPS, load graphicx instead
\usepackage{times}			% comment if you want LaTeX's default font
\usepackage{url}			% llt: nicely formatted URLs
\usepackage{dblfloatfix}	% allow placement of a page-width figure at top or bottom of page
% llt: Define a global style for URLs, rather that the default one

\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\bf\ttfamily}}}
\makeatother
\urlstyle{leo}

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}

% Make sure hyperref comes last of your loaded packages,
% to give it a fighting chance of not being over-written,
% since its job is to redefine many LaTeX commands.
\usepackage[pdftex]{hyperref}
\hypersetup{
pdftitle={SCS Conference Proceedings Format},
pdfauthor={LaTeX},
pdfkeywords={SCS, proceedings, archival format},
bookmarksnumbered,
pdfstartview={FitH},
colorlinks,
citecolor=black,
filecolor=black,
linkcolor=black,
urlcolor=black,
breaklinks=true,
}

% create a shortcut to typeset table headings
\newcommand\tabhead[1]{\small\textbf{#1}}

% create an affilitation superscript
\newcommand{\affiliation}[1]{\ensuremath{^{\textrm{#1}}}}

% End of preamble. Here comes the document.

\begin{document}
\title{\includegraphics[width=1.0\textwidth]{SimAUDLogo.png}\\\quad\\SCS-SimAUD Conference Proceedings Format}

% Replace "UniversityA", "CompanyA", "UniversityB" with institution-specific abbreviations.
\def\UniversityA{\affiliation{1}} 
\def\CompanyA{\affiliation{2}}
\def\UniversityB{\affiliation{3}}

\author{
	First Author Name\UniversityA
	,
	Second Author Name\CompanyA
	,
	Third Author Name\UniversityB
	\,and
	Fourth Author Name\CompanyA
	\\
	\\
\affaddr{\UniversityA}{Affiliation, City, Country, e-mail address}\\
\affaddr{\CompanyA}{Affiliation, City, Country, e-mail address}\\
\affaddr{\UniversityB}{Affiliation, City, Country, e-mail address}	
}

\maketitle

\begin{abstract}
This sample paper describes the formatting requirements for Conference Proceedings, and this sample file offers recommendations on writing for the worldwide readership. Please review this document even if you have submitted to SCS conferences before because some format details have changed relative to previous years.
\end{abstract}

\keywords{
	Guides; instructions; author's kit; conference publications;
	keywords should be separated by a semi-colon.	
	\textcolor{red}{Optional section to be included in your final version, but strongly encouraged..}
}

% ACM Classification Keywords
\category{I.6.1}{SIMULATION AND MODELING (e.g. Model Development). }
See: \url{http://www.acm.org/about/class/1998/} for more information and the full list of ACM classifiers and descriptors.
\textcolor{red}{Optional section to be included in your final version, but strongly encouraged.}

\section{Introduction}

This format is to be used for submissions that are published in the conference proceedings. We wish to give this volume a consistent, high-quality appearance. We therefore ask that authors follow some simple guidelines. In essence, you should format your paper exactly like this document. The easiest way to do this is simply to download a template from the conference web site, and replace the content with your own material. To obtain WORD DOC and Latex templates, please refer to the Author’s Kit on the SCS website.

\section{Page Size and Columns}

On each page your material should fit within a rectangle of 18 x 23.5 cm (7 in. x 9.25 in.), centered on a US letter page (21.59 x 27.94 cm; 8.5x11 inches), beginning 1.9 cm (.75 in.) from the top of the page, with a .85 cm (.33 in.) space between two 8.4 cm (3.3 in.) columns. Right margins should be justified (i.e. fully-justified), not ragged (except for the references section). Beware, especially when using this template on a Macintosh, Word can change these dimensions in unexpected ways. Please be sure your pdf is US letter and not A4. If your pdf are formatted for A4, the submission will be returned to you to fix within 2 days.

\section{Typeset Text}

Prepare your submissions on a word processor or typesetter. Please
note that page layout may change slightly depending upon the printer
you have specified. \LaTeX\ sometimes will create overfull lines
that extend into columns. To attempt to combat this, the .cls
file has a command, {\textbackslash}sloppy, that essentially asks
\LaTeX\ to prefer underfull lines with extra whitespace. For more
details on this, and info on how to control it more finely, check out
{\url{http://www.economics.utoronto.ca/osborne/latex/PMAKEUP.HTM}}.

\subsection{Title and Authors}

Your paper’s title, authors and affiliations should run across the full width of the page in a single column 17.8 cm (7 in.) wide. The title should be in Ariel 18-point bold; use Helvetica if Ariel is not available. Authors’ names should be in Times New Roman 12-point bold, and affiliations in Times New Roman 12-point (not bold, nor italic).

Please use full international addresses. Leave two 10-pt lines of white spaces below the last line of affiliations.

For the anonymous review copy of the manuscript, omit the authors’ names and affiliations. In place of the names, insert the submission number assigned by the online submission system.

\subsection{Abstract and Keywords}

Every submission should begin with an abstract of about 150 words (max. 200), followed by a set of keywords. The abstract and keywords should be placed in the left column of the first page under the left half of the title. The abstract should be a concise statement of the problem, approach and conclusions of the work described. It should clearly state the paper's contribution to the field of M\&S.

The first set of keywords will be used to index the paper in the proceedings. The second set are used to catalogue the paper in the ACM Digital Library. The latter are entries from the ACM Classification System \cite{acm_categories}.

\subsection{Normal or Body Text}

Please use a 10-point Times New Roman font or, if this is unavailable, another proportional font with serifs, as close as possible in appearance to Times New Roman 10-point. The Press 10-point font available to users of Script is a good substitute for Times New Roman. On a Macintosh, use the font named Times not Times New Roman. Please use sans-serif or non-proportional fonts only for special purposes, such as headings or source code text.

\subsection{First Page Copyright Notice}

This template has the correct SCS copyright notice in place (see page 1, bottom of column 1). Copyright will be held by SCS. Accepted work-in-progress and papers will be distributed in the Conference Publications. They will also be placed in the ACM Digital Library, as well as other prominent digital libraries, where they will remain accessible to thousands of researchers and practitioners worldwide. Leave 3 cm (1.25 in.) of blank space for the copyright notice at the bottom of the left column of the first page. In this template a floating text box will automatically generate the required space.

\subsection{Subsequent Pages}

On pages beyond the first, start at the top of the page and continue in double-column format. The two columns on the last page should be as close as possible to equal length.

\begin{figure}[!h]
\centering
\includegraphics[width=0.9\columnwidth]{Figure1}
\caption{With caption below, be sure to have a good resolution image (see below for image preparation instructions).}
\label{fig:figure1}
\end{figure}

\subsection{References and Citations}

Use a numbered list of references at the end of the article, ordered alphabetically by first author, and referenced by numbers in brackets [2, 4, 5, 7]. Kindly make the text of this section left-justified/ragged-right (instead of fully-justified as in the rest of the document), so that the increasing number of references/citations with web addresses/URLs do not have large word and letter spacing. For papers from conference proceedings, include the title of the paper and an abbreviated name of the conference (e.g., for Interact 2003 proceedings, use \textit{Proc. Interact 2003}). Do not include the location of the conference or the exact date; do include the page numbers if available. See the examples of citations at the end of this document. Within this template file, use the \texttt{References} style
for the text of your citation.

Your references should be published materials accessible to the public. Internal technical reports may be cited only if they are easily accessible (i.e., you provide the address for obtaining the report within your citation) and may be obtained by any reader for a nominal fee. Proprietary information may not be cited. Private communications should be acknowledged in the main text, not referenced (e.g., “[Robertson, personal communication]”).

\begin{table}
  \centering
  \begin{tabular}{|c|c|c|}
    \hline
    \tabhead{Objects} &
    \multicolumn{1}{|p{0.3\columnwidth}|}{\centering\tabhead{Caption --- pre-2002}} &
    \multicolumn{1}{|p{0.4\columnwidth}|}{\centering\tabhead{Caption --- 2003 and afterwards}} \\
    \hline
    Tables & Above & Below \\
    \hline
    Figures & Below & Below \\
    \hline
  \end{tabular}
  \caption{Table captions should be placed below the table.}
  \label{tab:table1}
  \hfill \break
  \centering
  \begin{tabular}{|c|c|c|c|c|}
	\hline
	\tabhead{} &
	\multicolumn{1}{|p{0.15\columnwidth}|}{\centering\tabhead{Anyone}} &
	\multicolumn{1}{|p{0.15\columnwidth}|}{\centering\tabhead{SN}} &
	\multicolumn{1}{|p{0.15\columnwidth}|}{\centering\tabhead{Specific}} &
	\multicolumn{1}{|p{0.15\columnwidth}|}{\centering\tabhead{No one}} \\
	\hline
	\textbf{Flight} & 45\% & 34\% & 18\% & 3\% \\
	\hline
	\textbf{City} & 47\% & 35\% & 14\% & 3\% \\
	\hline
  \end{tabular}
  \caption{Sharing travel plans}
  \label{tab:table2}
\end{table}

\section{Sections}

Headings of subsections should be in Ariel 9-point bold, all in capitals. Sections should be numbered.

\subsection{Subsections}

Headings of subsections should be in Ariel 9-point bold with
initial letters capitalized. Note: For sub-sections and sub-subsections, a word like \emph{the} or \emph{of} is not capitalized unless it is the first word of the heading.

\subsubsection{Sub-subsections}

Headings for sub-subsections should be in Ariel 9-point italic
with initial letters capitalized. Standard {\textbackslash}section,
{\textbackslash}subsection, and {\textbackslash}subsubsection commands
will work fine.

\begin{figure*}[ht!]
	\centering
	\includegraphics[width=1.0\textwidth]{Figure2}
	\centering
	\caption{Sample of a wide figure. Be sure to place at the top of the page or bottom of the page.}
	\centering
	\label{fig:figure2}
\end{figure*}

\section{Figures/Captions}

Place figures and tables at the top or bottom of the appropriate column or columns, on the same page as the relevant text (see Figure~\ref{fig:figure1}).

A figure or table may extend across both columns to a maximum width of 17.78 cm (7 in.). Captions should be Times New Roman 9-point bold (Caption Style in this template file). They should be numbered (e.g., “Table 1” or “Figure 2”), centered and placed beneath the figure or table. Please note that the words “Figure” and “Table” should be spelled out (e.g. use “Figure” rather than “Fig.”) wherever they occur.

Papers and notes may use color figures, which are included in the page limit; the figures must be readable when printed in black and white in the proceedings.

The paper may be accompanied by a short video figure up to five minutes in length. However, the paper should stand on its own without the video figure, as the video may not be available to everyone who reads the paper.

\subsection{Image Preparation}

Be sure your image has been resized to the appropriate printing resolution (usually 300 dpi).

\subsection{Table Style}
Tables should be prepared with consistent styling as specified with the cls file with captions marked clearly for interpretation. Long tables are recommended to be introduced by interrupting the multicolumn temporarily and/or as according to Figure ~\ref{fig:figure2}.
\section{Language, Style and Content}

The written and spoken language of SCS is English. Spelling and punctuation may use any dialect of English (e.g., British, Canadian, US, etc.) provided this is done consistently. Hyphenation is optional. To ensure suitability for an international audience, please pay attention to the following (note that while the items in this list are bulleted numbered lists are allowed):

\begin{itemize}
\item Write in a straightforward style.
\item Try to avoid long or complex sentence structures.
\item Briefly define or explain all technical terms that may be unfamiliar to readers.
\item Explain all acronyms the first time they are used in your text---e.g.,``Digital Signal Processing (DSP)''.
\item Explain local references (e.g., not everyone knows all city names in a particular country).
\end{itemize}

\begin{itemize}
\item Explain ``insider'' comments. Ensure that your whole audience understands any reference whose meaning you do not describe (e.g., do not assume that everyone has used a Macintosh or a particular application).
\item Explain colloquial language and puns. Understanding phrases like ``red herring'' may require a local knowledge of English. Humor and irony are difficult to translate.
\item Use unambiguous forms for culturally localized concepts, such as times, dates, currencies and numbers (e.g., ``1-5-97'' or ``5/1/97'' may mean 5 January or 1 May and ``12/10/11'' can be even more confusing, and ``seven o'clock'' may mean 7:00 am or 19:00). For currencies, indicate equivalences---e.g., ``Participants were paid 10,000 lire, or roughly \$5.''
\item Be careful with the use of gender-specific pronouns (he, she) and other gendered words (chairman, manpower, man-months). Use inclusive language that is gender-neutral (e.g., she or he, they, s/he, chair, staff, staff-hours, person-years). See~\cite{Schwartz:1995:GBF} for further advice and examples regarding gender and other personal attributes.
\item If possible, use the full (extended) alphabetic character set for names of persons, institutions, and places (e.g., Gr{\o}nb{\ae}k, Lafreni\'ere, S\'anchez, Universit{\"a}t, Wei{\ss}enbach, Z{\"u}llighoven, \r{A}rhus, etc.). These characters are already included in most versions of Times, Helvetica, and Arial fonts.
\end{itemize}

\section{Page Numbering, Headers and Footers}

Your final submission MUST NOT contain any footer or header information at the top or bottom of each page. The submissions will be paginated in a determined order by the chairs and page numbers added to the pdf during the compiling, indexing, and pagination processes. Comment out the {\textbackslash}pagenumbering command at the top of the document to remove page numbers.

\section{Producing and Testing PDF Files}

We recommend that you produce a PDF version of your submission well
before the final deadline. Test your PDF file by viewing or printing it with the same software we
will use when we receive it, Adobe Acrobat Reader Version 7. This is
widely available at no cost from~\cite{acrobat}. Note that most
reviewers will use a North American/European version of Acrobat
reader, which cannot handle documents containing non-North American or
non-European fonts (e.g. Asian fonts). Please therefore do not use
Asian fonts, and verify this by testing with a North American/European
Acrobat reader (obtainable as above). Something as minor as including
a space or punctuation character in a two-byte font can render a file
unreadable.

\section{Conclusion}

It is important that you write for the SCS audience. Please read previous years’ Proceedings to understand the writing style and conventions that successful authors have used. It is particularly important that you state clearly what you have done, not merely what you plan to do, and explain how your work is different from previously published work, (i.e. what is the unique contribution that your work makes to the field) ? Please consider what the reader will learn from your submission, and how they will find your work useful. If you write with these questions in mind, your work is more likely to be successful, both in being accepted into the Conference, and in influencing the work of our field.

\section*{ACKNOWLEDGMENTS}

Sample Text: We thank all volunteers, and all publications support and staff, who wrote and provided helpful comments on previous versions of this document. As well authors 1, 2, \& 3 gratefully acknowledge the grant from NSF (\# 1234 2012 ABC). This whole paragraph is just for example. Some of the references cited in this paper are included for illustrative purposes only.

\balance

% Balancing columns in a ref list is a bit of a pain because you
% either use a hack like flushend or balance, or manually insert
% a column break. http://www.tex.ac.uk/cgi-bin/texfaq2html?label=balance
% multicols doesn't work because we're already in two-column mode,
% and flushend isn't awesome, so we chose balance. See this
% for more info: http://cs.brown.edu/system/software/latex/doc/balance.pdf
%
% Note that in a perfect world balance wants to be in the first
% column of the last page.
%
% If balance doesn't work for you, you can remove that and
% hard-code a column break into the bbl file right before you
% submit:
%
% http://stackoverflow.com/questions/2149854/how-to-manually-equalize-columns-
% in-an-ieee-paper-if-using-bibtex
%

\bibliographystyle{scsBiblioStyle}
\bibliography{SampleReferences}

\centering
\large\bf The columns on the last page should be of approximately equal length.
\textcolor{red}{Remove these two lines from your final version.}

\end{document}

### 2020-03-28 old/01_introduction.tex
Initial Overleaf Import

It is obvious that building sector has witnessed massive development recently in the way by which building systems are managed in order to alleviate the massive energy consumption of this sector by better controlling the resources; providing sustainable and more efficient solutions; developing a better understanding of microclimate, buildings, and users' behaviours; and making better decisions based on either insightful ground-truth data (black-box approach), physics-based simulation models (white box approach) or a mixture of them (gray box approach). In this regard, it is worth mentioning that building sector is responsible for 30\% of the world energy consumption and a third of the associated CO2 emissions \citet{Iea2013TrackingMinisterial}.

On the other hand, the emergence of the micro-electro mechanical devices (MEMS) which lead to the ubiquitness of Internet-of-Things (IoT) devices (mobile devices, sensors, wearables, actuators ..etc) in the last few years to the extent that the number of interconnected IoT devices reached 11.2 billion by the time of writing this paper and continuing growing exponentially. These devices drastically changed computing paradigms, sensing and monitoring \citet{Ramaswamy2015InternetReview}, which enabled massive flow of data from each aspect of life such that the data collected during the last two decades exceeded that which is collected from the beginning of history. The biggest challenge ,though, is not the availability of data itself, but rather managing this big data: transferring, storing, preprocessing, wrangling and mining to obtain knowledge, optimization and control in a robust cyberinfrastructure. This lead to cloud computing or ubiquitous computing, that is , computing data in place, without paying much effort in transferring data to local storage/processing machines using scalable storage and computational power on demand maintained by professionals and provided in a form of Infrastructure as a Service (IaaS) and Platform as a service (PaaS) \cite{MellTheTechnology,Bhardwaj2010CLOUDIAAS,Dillon2010CloudChallenges}.

The convergence of those technologies however, requires users with proper domain knowledge alongside with programming or procedural thinking skills for automating, prototyping, analyzing, building work-flows using the massive amount of data and IoT sensors. Thus the term End-use programmer first introduced by \citet{Nardi1993AComputing} or Novice developer is used to describe people who are not professional developers yet able to create/modify software without significant knowledge of programming language and code structures \cite{MARGARETM.BURNETTANDCHRISTOPHERSCAFFIDIEnd-UserEd.}. In fact, most programs today are written by novice programmers \citet{Rothermel2011TheEngineering} as it had been estimated that by 2012, there would be less than 3 million professional programmers compared to more than 55 million end-use programmers, using spreadsheets, writing add-ons/plugins to support their work or add functionality to a software, running Matlab simulations, writing python codes, or IPython notebooks and so on \citet{ScaffidiEstimatingProgrammers}. The main difference between the end-use developer and the professional developer is the goal of the development. The former writes program to do specific task with the focus on getting this task done without paying so much attention to debugging, unit-testing or re-usability. however the latter develops, maintain, debug, and test a robust software for others to use. However they both face common challenges such as choosing which APIs, libraries, and functions to use; in addition, testing, verifying and debugging their codes regardless of the programming language used and its degree of complexity, for example: an end-use programmer could use general purpose language such as C++ to achieve specific task without the intent to publish the code for other to use. On the other side, a professional programmer could use a simple markup language such as HTML/CSS to develop a commercial website.

Each programming has what is so called a programming notation, this notation could be textual, diagrammatic, gesture-based .. etc. which is used to represent the state of the world. The selection of the proper programming notation to describe the problem is a trade-off between a number criteria that are based on cognitive psychology introduced by \citet{Green2004InstructionsDescriptions}, These are: \textbf{1)Viscosity (resistance to change)}, for example, if we need to change the interval time granularity of all sensors simultanously, how resistant would be the code? \textbf{2)Visibility (ability to view components easily)}, i.e. information are not hidden in encapsulations. \textbf{3)Premature commitment (constraints on the order of doing things)}, for example, the need to declare variable types or allocate memory initially. \textbf{4) Hidden dependencies (important links between entities are not visible)}, for instance, if there are interconnected entities, where the change one's value would affect the others, how visible is this interconnection?

\subsection{visual programming}

%There has been much research done on visual programming languages (VPLs) and en-vironments (VPEs). This has resulted in several different paradigms and styles of visual programming. We can classify VPLs based on their programming paradigm. Some of the most important VPL paradigms are constraint-based VPLs, data-flow VPLs, form-based and spreadsheet-based VPLs, imperative VPLs, and rule-based VPLs (Burnett & Baker, 1994). Costagolia et al. (2002) categorize VPLs based on the type of graphical notation they use. The Graph class of VPLs are those that consist of boxes and arrows connecting them. The Plex class covers the ones with flowchart style graphs with objects that have predefined number of attaching points. The Box class is mostly used for geographical sys- tems and consists of boxes that represent objects and spatial rules such as inclusion and intersection that represent queries. The Iconic class of VPLs uses icons for objects. And finally the Hybrid class uses features of two or more of above classes.
%needs rephrasing: 
Data-flow visual programming languages (DFVPLs)
Data-flow languages had been around for a while but the availability of cheap graphical
hardware in 1990s caused advances in data-flow visual language design (Johnston et al., 2004).

### 2020-03-28 paper_LateX/main.tex
Updates from Overleaf

\documentclass{scsSimAUDPaperFormat}

\usepackage[utf8]{inputenc}

\usepackage{listings}
\usepackage{xcolor}
\pagenumbering{arabic}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{1.0, 1.0, 1.0}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\small,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=4
}

% Beginning of preable.
% Ensure that the copyright notice matches the conference/symposium.
\copyrightnotice{
	SimAUD 2020 May 25-27 Vienna, Austria

	\copyright\,2020 Society for Modeling \& Simulation International (SCS)
}
% Load basic packages
\usepackage{balance}		% to better equalize the last page
\usepackage{graphics}		% for EPS, load graphicx instead
\usepackage{times}			% comment if you want LaTeX's default font
\usepackage{url}			% llt: nicely formatted URLs
\usepackage{dblfloatfix}	% allow placement of a page-width figure at top or bottom of page
% llt: Define a global style for URLs, rather that the default one

\usepackage{lipsum}  
\usepackage{soul}
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\bf\ttfamily}}}
\makeatother
\urlstyle{leo}

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}

% Make sure hyperref comes last of your loaded packages,
% to give it a fighting chance of not being over-written,
% since its job is to redefine many LaTeX commands.
\usepackage[pdftex]{hyperref}
\hypersetup{
pdftitle={SCS Conference Proceedings Format},
pdfauthor={LaTeX},
pdfkeywords={SCS, proceedings, archival format},
bookmarksnumbered,
pdfstartview={FitH},
colorlinks,
citecolor=blue,
filecolor=black,
linkcolor=blue,
urlcolor=blue,
breaklinks=true,
colorlinks=true,
}
% \hypersetup{
%     colorlinks=true,
%     linkcolor=blue,
%     filecolor=magenta,      
%     urlcolor=cyan,
% }
% create a shortcut to typeset table headings
\newcommand\tabhead[1]{\small\textbf{#1}}

% create an affilitation superscript
\newcommand{\affiliation}[1]{\ensuremath{^{\textrm{#1}}}}

% End of preamble. Here comes the document.
% \tolerance=1
% \emergencystretch=\maxdimen
% \hyphenpenalty=10000
% \hbadness=10000
\begin{document}
% \title{\includegraphics[width=1.0\textwidth]{SimAUDLogo.png}\\\quad\\BuildFit: A Model-Veiw-Controller (MVC) Open Platform for Building-Lifecycle Data Analysis and Energy Modelling }

\title{\includegraphics[width=1.0\textwidth]{SimAUDLogo.png}\\\quad\\A Three-Tier Architecture Visual-Programming Platform for Building-Lifecycle Data Management }

% Replace "UniversityA", "CompanyA", "UniversityB" with institution-specific abbreviations.
\def\UniversityA{\affiliation{1}} 
\def\CompanyA{\affiliation{2}}
\def\UniversityB{\affiliation{3}}

\author{
% 	Author1\UniversityA
% 	,
% 	Author2\UniversityA
% 	,
% 	Author3\UniversityA
% 	\\
% 	\\
% \affaddr{\UniversityA}{Department, School, University, Country, zipcode.}\\
}

\author{
	Mahmoud M. Abdelrahman\UniversityA
	,
	Sicheng Zhan\UniversityA
	,
	Adrian Chong\UniversityA
	\\
{\\^1 \textbf{\large Department of Building, School of Design and Environment,}\\The National University of Singapore, 4 Architecture Drive, Singapore 117566.}\\
}

\maketitle

\begin{abstract}
	In this paper, we present a platform that integrates three main aspects in the building industry: 1) Building data from both IoT devices and Building Management System (BMS), 2) Building Energy modeling and simulation engine, and 3)Data analysis and optimization libraries. All of which are combined in a three-tier architecture cloud platform. The platform aims to provide useful representations of the data to different stakeholders. We defined three main types of stakeholders. Each stakeholder uses the platform differently: (1) End-use programmers, who use visual programming and textual programming interfaces to perform computational tasks, (2) Dashboard viewers who are interested in viewing insightful real-time data about performance in the form of charts and diagrams, and (3) Data feedback inputters such as occupants to give feedback or fill questionnaires. The three-tier architecture enables the spatial and physical separation of the databases, the computational engines, and the user-interfaces. This separation resulted in some advantages such as flexibility, scalability (horizontal and vertical), reusability, and latency reduction. \hl{Currently, the platform is in the final stage of development. The following stage includes community testing and user experience enhancement.}
\end{abstract}

\keywords{
	three-tier architecture;
	n-tier architecture;
	Building Energy Modelling;
	BEM;
	building lifecycle;
	actors;
	presentation layer;
	application layer;
	data layer
}

% ACM Classification Keywords
\category{I.6.1}{SIMULATION AND MODELING}
Computing methodologies ~ Model development and analysis - 
Software and its engineering ~ Visual languages
% See: \url{http://www.acm.org/about/class/1998/} for more information and the full list of ACM classifiers and descriptors.
% \textcolor{red}{Optional section to be included in your final version, but strongly encouraged.}
\section{Introduction}
The building sector has witnessed immense development recently in the way by which building systems are managed \cite{ WongIntelligentReview}. This development aimed at alleviating the significant environmental impact of this sector (30\% of the world energy consumption and a third of the associated CO2 emissions \cite{Iea2013TrackingMinisterial}). Decreasing this impact could be achieved by better controlling the resources \cite{Allcott2010BehaviorPolicy}; providing sustainable, and more efficient solutions \cite{Zhang2019WholeLearning}; developing a better understanding of different deterministic and stochastic aspects of the built environment \cite{Brohus2012QuantificationApproach,ReviewsStochasticReview, USDepartmentofEnergy2018TechnologyReport, Chong2015UncertaintyApproach}. In addition, making better decisions based on mining ground-truth data (black-box approach)\cite{Molina-Solana2017DataReview}, physics-based simulation models (white-box approach)\cite{TardioliDataLevel,Molina-Solana2017DataReview} or both of them (gray-box approach)\cite{Zhang2019WholeLearning}.

The emergence of the Internet of Things (IoT) devices has enabled a massive amount of data, which posed some challenges. The data collected during the last two decades exceeded that which has ever been collected in history\cite{Ramaswamy2015InternetReview}. Two significant challenges, other than the availability of data, are to be addressed. On the one hand, managing this big data: transferring, storing, preprocessing, wrangling and mining, optimization, and control in a robust cyber-infrastructure. This lead to cloud computing or ubiquitous computing, that is, computing data in place, without paying much effort in transferring data to local storage/processing machines using scalable storage and computational power on demand maintained by professionals \cite{MellTheTechnology,Bhardwaj2010CLOUDIAAS,Dillon2010CloudChallenges}. On the other hand, delivering useful information to different stakeholders based on their use is yet another challenge.

% Making use of this massive amount of data from the built environment requires 
"Data is not information; data must be presented in a usable form before it becomes information" \cite[p.134]{Reen1996UsabilityFramework}. Raw data from the built environment varies in its degree of usefulness to different stakeholders (actors). "Usability" is different for different stakeholders. For instance, A Building Energy Modeller (BEM) requires data such as Green Building eXtensible Markup Language (gbXML) \cite{GbXMLSchema}, schedules of operations, set-points, number of occupants,etc.. At the same time, a Facility Manager (FM) would be more interested in reducing maintenance costs by fault detection and diagnostics (FDD)\cite{Zibion2018DevelopmentInformation} algorithms and dashboards. This difference in uses requires users with proper domain knowledge alongside with programming or procedural thinking skills for automating, prototyping, analyzing, building work-flows using the big data and IoT sensors. At the same time, they do not need to be professional programmers, but rather End-use programmers.

The term \textit{End-use programmer} (or Novice developer) first introduced by \cite{Nardi1993AComputing} is used to describe non-professionals without programming and code structures knowledge \cite{MARGARETM.BURNETTANDCHRISTOPHERSCAFFIDIEnd-UserEd.}. Most programs today are written by novice programmers \cite{Rothermel2011TheEngineering} who use spreadsheets, writing add-ons/plugins to support their work or add functionality to the software, running MATLAB simulations \cite{MATLABSimulink}, writing python codes, or IPython notebooks \cite{ScaffidiEstimatingProgrammers}. The main difference between the end-user developer and the professional developer is the goal of the development. The former writes a program focusing on getting tasks done without paying attention to debugging, unit-testing, or re-usability. However, the latter develops, maintain, debug, and test a robust software for others to use\cite{LiebermanEnd-userDevelopment}. End-use development mostly involves modifying or extending a software artifact (known as programming by example, or programming by demonstration). For example, \textit{Extended annotation or parameterization}: whereas a user can define a new functionality by selecting a readily developed set of functions by other users and stored in shared repositories \cite{Lieberman2006End-UserParadigm}. To make this task handy to end-use programmers, a proper programming notation should be utilized.

\textit{Programming notation} is the way by which a programming language is used to represent the state of the world\cite{Green2004InstructionsDescriptions}). The selection of the proper programming notation (e.g., textual, diagrammatic, or gesture-based) to describe the problem is a trade-off between several evaluation criteria\cite{Green2004InstructionsDescriptions}. This trade-off should lead non-specialist to find the programming environment easy-to-use and easy-to-understand.

A large body of studies have addressed some difficulties related to the everyday programming tasks such as, but not limited to, code navigation \cite{DeLine2006CodeCode}, and hidden dependencies. A study conducted by Bragdon et al. \cite{Bragdon2010CodeMaintenance} that uses visual programming 2d spatially connected blocks of codes where it is possible to track each function in the form of bubble showed that visual programming significantly improve code understanding with less code navigation time.

Visual Programming Language (VPL), also known as box-and-wire programming or data-flow programming utilizes user-friendly graphical elements to display the flow of data between different components (Figure \ref{fig:vpl_example}). To date, there has been little agreement on the superiority of visual programming languages (VPLs) over the textual programming languages (TPLs). Green et.al. \cite{PDFConjecture} and Moher et.al. \cite{Moher1993ComparingPrograms} adopted this stance. However, \cite{MENZIES2002EVALUATIONLANGUAGES} argued that VPLs could be significantly useful in motivating beginners to learn to program as they are informative in the sense of spatial reasoning and ideas generation. However, he argued that those advantages are not generalized and should not be isolated from the task being studied. Also, TPL is more productive in terms of large-scale and complex software development tasks. There is no conclusive evidence of the superiority of one over the other. Thus, a hybrid VPL/TPL is proven to be suitable amongst users. Many software enables this type of scripting which gained wide popularity such as Rhinoceros VPL Grasshopper\cite{Bachman2017Grasshopper:3D,2011bGrasshopperRhino} whose user-community extended its limits by contributing to developing TPL based functions amongst others for building and urban simulation \cite{RoudsariLadybug:Design, PeronatoIntegratingCitySim,Koltsova2011ComponentsGeometry}, daylight analysis \cite{JakubiecDIVAENERGYPLUS,LagiosANIMATEDRADIANCE/DAYSIM}, Machine learning\cite{Abdelrahman2017EnhancingLanguage,Abdelrahman2019ANT:Development}.

\hl{This research addresses two primary problems:}
\begin{enumerate}
    \item \hl{Managing buildings' big data requires flexibility and scalability.}
    %Maybe a better problem the VP addresses is the ability to connect data to mode
    \item \hl{Different users are use data differently.}
\end{enumerate}

\begin{figure}
\centering
\includegraphics[width=0.9\columnwidth]{imgs/vpl_example.png}
\caption{\hl{A screenshot from our platform indicating a parametric simulation process on the cloud using (BuildSimHub)}. The figure is an example of Visual programming Language (also known as box-and-wire programming notation, and data-flow programming) where blocks of code functions are encapsulated in the boxes (known as components), while data flows from one or more component output variable to other component input variable. A component can hold as many inputs as needed, while the code behind each component follows a specific schema. Some components are used only as input components such as "file, numerical, panel" and some components work as output visualizations such as "panel, 3d visualization canvas, plotting components .."}
\label{fig:vpl_example}
\end{figure}
We introduce a Three-tier architecture web platform as a resolution to these problems. The objectives of this research are: (1) Making IoT data from the built environment useful to different stakeholders, (2) An Open platform for developing and sharing different models amongst end-use programmers. (3) Provide flexibility and scalability by separating the platform into three distributed layers. The rest of the paper is structured as follows: In section \ref{section1}, we explain the three-tier architecture. The components of the three-tier architecture are explained in details in the subsequent sections \ref{section3} (Actors), \ref{sec:presentationLayer} (Presentation Layer), \ref{sec:applicationlayer} (Application Layer), and \ref{sec:datalayer} (Data Layer).

\section{Three-Tier Architecture}
\label{section1}
\textit{Three-tier architecture} is a client-server software architecture pattern that has several potentials in distribution applications \cite{Booch1994OBJECT-ORIENTEDEDITION}. The key aspect of this architecture is that it enables the reusability of program building blocks (also referred to as components) such as sharing software components at run time, replicating the same component, controlled adaptation of code, or independent adaptation of components \cite{Taylor1998ThePerspective,Wijegunaratne1998DistributedEngineering}. This pattern consists of three functionally separated layers \cite{Schuldt2017Multi-tierArchitecture} (Figure \ref{fig:figure1}), those are: \textbf{1) Presentation layer} (the client-side), \textbf{2) Application layer} (also known as business logic, controllers and process management layer), and \textbf{3) Data layer} (also known as data storage). The presentation layer constitutes the user-interface side of the application. All human-computer interactions (HCI) happen on this layer. On the other side, the Business logic layer consists of the core engine where component functions that carry out the workload by receiving requests from the presentation layer get the relevant data from the Data layer and process this data then, sends back the response to the presentation layer. Finally, the Data layer consists of data querying (acquire from a data source), storage (stored in the relational database on a local server), and accessing (feed to the user). Each of these three tires is discussed in detail in the subsequent sections.

\begin{figure}
\centering
\includegraphics[width=0.9\columnwidth]{imgs/three_tier_architecture_summary.png}
\caption{Three-tier architecture structure of the platform}
\label{fig:figure1}
\end{figure}

Advantages of using three-tier architecture \cite{Furht2010HandbookComputing}:
\begin{enumerate}
    \item Reusability: The use of a modular component-function system enables many users/developers to contribute to the development. This contribution is shared in a public repository to be reusable by other users with small or no change
    \item Scalability (both horizontally and vertically) is another essential feature of using three-tier architecture because of using distributed servers as well as because of its separation nature. Horizontal Scalability is achieved by adding more nodes of the same types where required. While the Vertical Scalability is achieved by adding more resources to a host node on demand. On the other hand, separating different tiers allows scaling each one independently depending on the needs at any given time. 
    % The more the new users, nodes, or components are added, the more the resources are scaled out horizontally (adding new resources of the same type) to fit the load. 
    \item Flexibility: As server nodes that are used in the application layer could be developed, configured and tested separately without affecting any of the other layers, and then it could be added to the system on demand. Readily PaaS (Platform as a Service) is used to maintain consistency and Scalability. 
    \item Latency reduction: As the nodes are distributed on data centers that are spatially close to the end-user as possible. This is basically handled by adopting open PaaS (Platform as a Service) where the infrastructure complexity of servers are maintained and optimized by professionals. 
    \item Anytime data processing regardless of the user's connection speed. The connection between the application layer and the data layer is separated from the presentation layer, reducing the bandwidth load on the user's side.

\end{enumerate}

\section{actors}
\label{section3}
We use the term "Actor" to refer to different users/stakeholders within the built environment. "Usability" is the critical factor in obtaining "information" from data. Data obtained from the built environment does not hold equal usefulness for all stakeholders. Furthermore, in its raw format, IoT data consists of many problems, including noise, missing data, non-valid data, ill-labeled data points, duplicates, and non-standardized IoT representation. These problems should be dealt with before delivering this data to non-expert users. \hl{We define some actors or stakeholders who are involved in the building's life cycle energy modeling and data analysis and their corresponding data usage based on a systematic review conducted by Zou et.al \cite{Zou2018ReviewPerspectives} of 10 years publications till 2017 and  using Natural language processing (NLP) \cite{Abdelrahman2020BuildingWord-Embeddings}.

% \begin{figure}[h]
% \centering
% \includegraphics[width=0.9\columnwidth]{imgs/sim_art_eng.png}
% \caption{Using word embeddings, it is possible to do arithmetic vector operations on words, e.g. 'artist' + 'engineer' $\sim$ 'architect','designer', and - not surprisingly - 'scientist'.}
% \label{reasonablemeaining}
% \end{figure}

% \begin{figure}[h]
% \centering
% \includegraphics[width=0.8\columnwidth]{imgs/stakeholders.png}
% \caption{A list of \textit{filtered actors} (They are manually filtered because the original list consists of many words that do not represent actors.) words similar to the word "Stakeholder" are extracted from NLP mining building-related articles. The darker the color, the more the similarity index. The thickness of the edge (as well as the label on the edge) show the similarity index (i.e., this word appears more frequent in the context where "stakeholder" appears) \cite{Abdelrahman2020BuildingWord-Embeddings}.}

% \label{fig:figure4}
% \end{figure}

% \begin{figure}[h]
% \centering
% \includegraphics[width=0.8\columnwidth]{imgs/stakeholder3.png}
% \caption{ After narrowing down the scope of similarity search (by aggregating more keywords related to 'stakeholders.') 
% \cite{Abdelrahman2020BuildingWord-Embeddings}
% . The darkness of the color means a higher similarity, and the thickness of the edge represents a higher similarity as well.}
% \label{fig:figure5}
% \end{figure}

Then, we identified three main data-related actions, namely, \textbf{End-use programming}, \textbf{Data monitoring}, and \textbf{Data input}. Different stakeholders are clustered based on these three activities (Figure \ref{fig:figure6}). Then, these activities are reflected in the presentation layer \textit{(explained in section \ref{sec:presentationLayer})}  as three major components: 1) Hybrid VPL/TPL interface, 2) Interactive, shareable, embedded dashboards, and 3) Shareable, embedded forms. The interface of the platform is shown in figure \ref{fig:platformInterface}.}

\begin{figure}[h]
\centering
\includegraphics[width=0.8\columnwidth]{imgs/presentation_layer.png}
\caption{Actors are functionally clustered into three categories: Data monitoring, Data input, and End-use programming. Those categories constitute the Presentation layer.}
\label{fig:figure6}
\end{figure}

\section{Presentation Layer}
\label{sec:presentationLayer}
The presentation layer acts as the interface for the users. Each new project has a unique global unique identification (GUID), which is stored on the data layer and could be called using its GUID. Three main functions used in the presentation layer: (1) Visual/Textual programming interface, (2) dashboards, and (3) forms are used.

\begin{figure*}[h]
\centering
\includegraphics[width=\linewidth]{imgs/platform_interface.png}
\caption{The main interface functions}
\label{fig:platformInterface}
\end{figure*}

\subsection{VPL/TPL interface}
Both the visual and the textual programming interface use two main languages: Python and JavaScript. However, the selection of which is based on the complexity of the task and the response time required. For example: if the component function requires a real-time reaction, then it is more suitable to use a JavaScript component/script. We refer to the component in this case as \textit{"Shallow Function"}. While if the function requires heavy calculation such as Machine Learning (ML), or Energy Simulation (ES), then Python-based components/scripts are used and are referred to as \textit{"Deep Functions"}. Examples are shown in figure \ref{fig:deep-shallow}.

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{imgs/shallow_deep.png}
\caption{Two examples of Shallow and Deep functions. 1. The deep function is Python-based, and hosted on the application layer, the "play button" on the bottom of the component must be clicked to run the deep function. 2. The shallow function is JavaScript based and is hosted on the front-end. However, all the shallow functions are stored in the data layer and follow specific schema. The shallow functions are used to implement real-time actions, such as arithmetic operations, and JavaScript Object Notation (JSON) parsing. In this figure, the deep function on the left uses OSISoft Python API to request time-series data from the data layer and outputs it as a JSON object. Then, the shallow component on the right parses the JSON object and converts it into different formats, including plotting.}
\label{fig:deep-shallow}
\end{figure}

Each component must follow specific abstraction schema that defines its structure and relationships as well as its types. Mainly, it consists of inputs, the function body, and outputs. However, other information must be provided when defining a new component e.g., The \texttt{dataflowType}: either shallow or deep, the component \texttt{type}: numeric, panel, optionList, ListItem, Plot, Generic, etc., the \texttt{category} where this component falls into, and other supplementary features such as the color, documentation, and license.

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{imgs/component.png}
\caption{The data flows within components from left to the right. Each input of the component either carries a default value or receive value from other component's output, this value is stored in the input until the component runs, then the input variables are processed by calling the corresponding function. After the function is called, the return output of the function is stored back into the output of the component unless this output is connected to other component's input, it runs the other component automatically.}
\label{fig:component}
\end{figure}

Each component has a unique GUID on a project level. This GUID is used to trigger the component and call its inputs and outputs using the TPL panels. For example: the deep component (Figure \ref{fig:deep-shallow}) has a GUID : \texttt{'c56ad1cf-47ea-4fe3-805b-84d104ecff8b'} could be triggered using the Python API . This allows the end-use programmer to extend the functionality of the components by running blocks of codes either before running the component (i.e. doing preprocessing to the inputs) or after running the component (i.e. doing post-processing to the outputs) using the functions \texttt{before(callback)} and \texttt{after(callback)} as shown in listing \ref{lst:trigger_vpl} and figure \ref{fig:tpl_interface}.

\begin{lstlisting}[style=mystyle,
language=Python,
caption={Triggering a VPL component using TPL Pyton interface},
label={lst:trigger_vpl}]
import buildFit as bf
import json

component = bf.getComponent.by_guid("c56ad1cf-47ea-4fe3-805b-84d104ecff8b")
if component.inputs[0] == None:
    compoent.inputs[0] = "http://google.com"

def preprocessInputs(input1):
    '''This function is applied to the input before running the component'''
    return input1

def postprocessOutputs(output1):
    '''This function is applied to the output after running the component'''
    return json.parse(output1)

inp1 = component.before(preprocessInputs, component.inputs[0])
out1 = component.after(postprocessOutputs, component.outputs[0])
\end{lstlisting}

\begin{figure*}[h]
\centering
\includegraphics[width=\linewidth]{imgs/tpl_interface.png}
\caption{TPL interface using Python script. The python script enables reading, writing inputs and outputs of different components, as well as adding pre/post processing functions to the inputs/outputs.}
\label{fig:tpl_interface}
\end{figure*}
\subsection{Dashboard and forms}

\label{sec:applicationlayer}
The dashboard and forms are located in the same tab called 'Dashboard'. It is an information management tool directed to stakeholders who are not involved directly in the development of the project i.e., to track performance, metrics, and other key data points; or to get feedback and other user inputs (questionnaires or thermal comfort feedback). The project owner does the design of the dashboard, using the input components (e.g., numeric slider, optionList, listView, RadioButtons, and  Panels ) and the output components (e.g., Panels, Plots, 3D views, 2D plans, images, videos etc.). Then, the dashboard could be shared with public or specific people to view or interact. It can also be embedded within other websites.
\section{Application Layer}
The application layer receives the deep function requests from the presentation layer in the form of a JSON object following specific schema. On the one hand, If there are data-related processes, it sends a request to the data layer (explained in detail in section \ref{sec:datalayer}. On the other hand, if there are no database-related processes, the JSON object consisted of the inputs and the component function callback. The function then starts to operate in three cases:
\begin{enumerate}
    \item It runs the function directly from the node. 
    \item It starts other cloud engines to run the functions. 
    \item It uses third party engines (e.g. BuildSimHub) to perform the operation. 
\end{enumerate}
Consequently, the function response back to the presentation layer as a JSON object with the outputs (if any), Errors, and logs. The response JSON object also follows a predefined schema as shown in figure \ref{fig:component}. The whole process is illustrated in figure \ref{fig:structure} (steps: 1, 2, 3, 8, 9).
\begin{figure*}[ht]
\centering
\includegraphics[width=\linewidth]{imgs/allStructure.png}
\caption{This figure shows the flow of data within the three tiers: (1) The actor interact with the presentation layer three ways: programming, viewing dashboards, or giving feedback; (2)The user interaction results in sending requests to the application layer to be processed; (3)The application layer starts processing inputs and relevant functions; (4) If there is any required data from the databases, a QUERY is sent to the data layer; (5) then, the data layer respond with the corresponding data from different databases (6,7); (8) The application layer then runs the required components using the distributed engines; (9) The output of step (7) is responded back to the presentation layer along with the logs/errors in JSON format. higher resolution image can be downloaded \href{https://user-images.githubusercontent.com/6969514/72152397-cee71700-33e5-11ea-9108-c6823d2be504.png}{here}
}
\label{fig:structure}
\end{figure*}

\section{Data Layer}\label{sec:datalayer}

There are four major types of data involved in this platform: metadata of the users and projects, metadata of the buildings, building models, and building operational data. The data layer has three main functions: \textbf{Data querying}: to acquire data from multiple data sources, \textbf{Data storage}: to store different types of data, and \textbf{Data feed}: to respond to the requests from the application layer.\par

The metadata and models are either input by the users through the presentation layer or assigned by the application layer. These data are mainly text. Once passed to the data layer, they are static and stored in the relational databases (Figure \ref{fig:relationDatabase}). As for the building operational data, the time series data comes from servers of different Building Management Systems. BMS in different buildings are various, in terms of data structure, sampling rate, communication protocol, etc., making data querying a troublesome task. The platform dealt with this by deploying the PI system from OSIsoft \cite{PiSystem}, which queries data from different types of servers, such as BACnet (Building Automation and Control networks) and OPC (Open Platform Communications), and stores the compressed data on the local server.\par
\begin{figure*}
\includegraphics[width=\linewidth]{imgs/uml_relationship.jpeg}
\caption{Relational database: A higher resolution image can be downloaded  \href{https://user-images.githubusercontent.com/6969514/72235771-e9e89f80-360e-11ea-9cf7-91c0f521576c.jpeg}{here}
}
\label{fig:relationDatabase}
\end{figure*}
Data exchange between the application layer and the data layer is done through RESTful API and mainly in JSON format. For example, if a user wants to see the energy consumption trend of a building, he/she will select the data point and define the time period in VPL canvas. The deep functions in the application layer will get the information and accordingly send the request. The API will retrieve data from the server and send it back as a JSON file, which will then be plotted in the canvas.
\section{Case study} \label{section:casestudy}
In this section, we introduce a case-study to evaluate our platform.

\section{Conclusion}
In this paper, we explained an approach for applying Client/Server based architecture called 3-tier architecture (summarized in figure \ref{fig:structure}). This approach is used for managing data from the built environment using a cloud-based user-friendly visual programming interface. This approach depends on separating the client-side (called the presentation layer) from the back-end engines (the application layer) and the databases (the data layer). This separation eased the distribution of computation power over many nodes without compromising the efficiency of the other layers. Furthermore, it overcame some problems related to latency and connection speed. Moreover, flexibility and scalability are two key features of this type of architecture.

Future development includes enabling real-time teamwork, version controls, besides continuous testing and user-experience improvements.

\section*{ACKNOWLEDGMENTS}
% This paper is a part of a project funded by the Ng Teng Fong Charitable Foundation (NTFCF) research funding.
\clearpage
\balance

\bibliographystyle{scsBiblioStyle}

\bibliography{references.bib,./references2.bib,SampleReferences.bib}
\end{document}

### 2020-03-28 paper_LateX/main.tex

@@
 The API will retrieve data from the server and send it back as a JSON file, which will then be plotted in the canvas.
-\section{Case study} \label{section:casestudy}
-In this section, we introduce a case-study to evaluate our platform.
+\section{Use cases} \label{section:casestudy}
+In this section, we introduce three use-cases to evaluate our platform.
+The first is a parametric energy simulation of a small office building from ANSI/ASHRAE/IES Standard 90.1 commercial reference buildings
 

### 2020-03-29 paper_LateX/main.tex
Updates from Overleaf

--- 2020-03-28 paper_LateX/main.tex
@@
 On the one hand, managing this big data: transferring, storing, preprocessing, wrangling and mining, optimization, and control in a robust cyber-infrastructure.
-This lead to cloud computing or ubiquitous computing, that is, computing data in place, without paying much effort in transferring data to local storage/processing machines using scalable storage and computational power on demand maintained by professionals \cite{MellTheTechnology,Bhardwaj2010CLOUDIAAS,Dillon2010CloudChallenges}.
+This lead to cloud computing or ubiquitous computing, that is, computing data in place, without paying much effort in transferring data to local storage/processing machines using scalable storage and computational power on demand maintained by professionals \cite{MellTheTechnology,Bhardwaj2010Cloud,Dillon2010CloudChallenges}.
 On the other hand, delivering useful information to different stakeholders based on their use is yet another challenge.
@@
 "Usability" is different for different stakeholders.
-For instance, A Building Energy Modeller (BEM) requires data such as Green Building eXtensible Markup Language (gbXML) \cite{GbXMLSchema}, schedules of operations, set-points, number of occupants,etc..
+For instance, A Building Energy Modeller (BEM) requires data such as Green Building eXtensible Markup Language (gbXML) \cite{GreenBuildingXMLgbXMLSchema2019GbXMLSchema}, schedules of operations, set-points, number of occupants,etc..
 At the same time, a Facility Manager (FM) would be more interested in reducing maintenance costs by fault detection and diagnostics (FDD)\cite{Zibion2018DevelopmentInformation} algorithms and dashboards.
@@
 
-The term \textit{End-use programmer} (or Novice developer) first introduced by \cite{Nardi1993AComputing} is used to describe non-professionals without programming and code structures knowledge \cite{MARGARETM.BURNETTANDCHRISTOPHERSCAFFIDIEnd-UserEd.}.
-Most programs today are written by novice programmers \cite{Rothermel2011TheEngineering} who use spreadsheets, writing add-ons/plugins to support their work or add functionality to the software, running MATLAB simulations \cite{MATLABSimulink}, writing python codes, or IPython notebooks \cite{ScaffidiEstimatingProgrammers}.
+The term \textit{End-use programmer} (or Novice developer) first introduced by \cite{Nardi1993AComputing} is used to describe non-professionals without programming and code structures knowledge \cite{InteractionDesignFoundation2014End-UserEd.}.
+Most programs today are written by novice programmers \cite{Rothermel2011TheEngineering} who use spreadsheets, writing add-ons/plugins to support their work or add functionality to the software, running MATLAB simulations \cite{Mathworks2016MATLABSimulink}, writing python codes, or IPython notebooks \cite{ScaffidiEstimatingProgrammers}.
 The main difference between the end-user developer and the professional developer is the goal of the development.
@@
 Green et.al.
-\cite{PDFConjecture} and Moher et.al.
+\cite{Green1991ComprehensibilityConjecture} and Moher et.al.
 \cite{Moher1993ComparingPrograms} adopted this stance.
@@
 Thus, a hybrid VPL/TPL is proven to be suitable amongst users.
-Many software enables this type of scripting which gained wide popularity such as Rhinoceros VPL Grasshopper\cite{Bachman2017Grasshopper:3D,2011bGrasshopperRhino} whose user-community extended its limits by contributing to developing TPL based functions amongst others for building and urban simulation \cite{RoudsariLadybug:Design, PeronatoIntegratingCitySim,Koltsova2011ComponentsGeometry}, daylight analysis \cite{JakubiecDIVAENERGYPLUS,LagiosANIMATEDRADIANCE/DAYSIM}, Machine learning\cite{Abdelrahman2017EnhancingLanguage,Abdelrahman2019ANT:Development}.
+Many software enables this type of scripting which gained wide popularity such as Rhinoceros VPL Grasshopper\cite{Bachman2017Grasshopper:3D,McNeel2010GrasshopperRhino} whose user-community extended its limits by contributing to developing TPL based functions amongst others for building and urban simulation \cite{RoudsariLadybug:Design, PeronatoIntegratingCitySim,Koltsova2011ComponentsGeometry}, daylight analysis \cite{Jakubiec2011DIVAEnergyPlus,Lagios2010AnimatedDaysim}, Machine learning\cite{Abdelrahman2017EnhancingLanguage,AbdelRahman2017GH_CPython:Grasshopper,Abdelrahman2019ANT:Development}.
 
-\hl{This research addresses two primary problems:}
+This research addresses two primary problems:
 \begin{enumerate}
-    \item \hl{Managing buildings' big data requires flexibility and scalability.}
+    \item Managing buildings' big data requires flexibility and scalability.
     %Maybe a better problem the VP addresses is the ability to connect data to mode
-    \item \hl{Different users are use data differently.}
+    \item Different users use data differently.
 \end{enumerate}
@@
 \includegraphics[width=0.9\columnwidth]{imgs/vpl_example.png}
-\caption{\hl{A screenshot from our platform indicating a parametric simulation process on the cloud using (BuildSimHub)}.
+\caption{A screenshot from our platform indicating a parametric simulation process on the cloud using (BuildSimHub).
 The figure is an example of Visual programming Language (also known as box-and-wire programming notation, and data-flow programming) where blocks of code functions are encapsulated in the boxes (known as components), while data flows from one or more component output variable to other component input variable.
@@
 \label{section1}
-\textit{Three-tier architecture} is a client-server software architecture pattern that has several potentials in distribution applications \cite{Booch1994OBJECT-ORIENTEDEDITION}.
+\textit{Three-tier architecture} is a client-server software architecture pattern that has several potentials in distribution applications \cite{Booch2008Object-orientedEdition}.
 The key aspect of this architecture is that it enables the reusability of program building blocks (also referred to as components) such as sharing software components at run time, replicating the same component, controlled adaptation of code, or independent adaptation of components \cite{Taylor1998ThePerspective,Wijegunaratne1998DistributedEngineering}.
@@
 Each of these three tires is discussed in detail in the subsequent sections.
+A summarized workflow is illustrated in figure \ref{fig:structure}.
 
@@
 \end{figure}
+
+\begin{figure*}[ht]
+\centering
+\includegraphics[width=0.8\linewidth]{imgs/allStructure.png}
+\caption{This figure shows the flow of data within the three tiers: (1) The actor interact with the presentation layer three ways: programming, viewing dashboards, or giving feedback; (2)The user interaction results in sending requests to the application layer to be processed; (3)The application layer starts processing inputs and relevant functions; (4) If there is any required data from the databases, a QUERY is sent to the data layer; (5) then, the data layer respond with the corresponding data from different databases (6,7); (8) The application layer then runs the required components using the distributed engines; (9) The output of step (7) is responded back to the presentation layer along with the logs/errors in JSON format.
+higher resolution image can be downloaded \href{https://user-images.githubusercontent.com/6969514/72152397-cee71700-33e5-11ea-9108-c6823d2be504.png}{here}
+}
+\label{fig:structure}
+\end{figure*}
 
@@
 These problems should be dealt with before delivering this data to non-expert users.
-\hl{We define some actors or stakeholders who are involved in the building's life cycle energy modeling and data analysis and their corresponding data usage based on a systematic review conducted by Zou et.al \cite{Zou2018ReviewPerspectives} of 10 years publications till 2017 and  using Natural language processing (NLP) \cite{Abdelrahman2020BuildingWord-Embeddings}.
+We define some actors or stakeholders who are involved in the building's life cycle energy modeling and data analysis and their corresponding data usage based on a systematic review conducted by Zou et.al \cite{Zou2018ReviewPerspectives} of 10 years publications till 2017 and  using Natural language processing (NLP) \cite{Abdelrahman2020BuildingWord-Embeddings}.
 
@@
 Then, these activities are reflected in the presentation layer \textit{(explained in section \ref{sec:presentationLayer})}  as three major components: 1) Hybrid VPL/TPL interface, 2) Interactive, shareable, embedded dashboards, and 3) Shareable, embedded forms.
-The interface of the platform is shown in figure \ref{fig:platformInterface}.}
+The interface of the platform is shown in figure \ref{fig:platformInterface}.
 
@@
 
-\begin{figure*}[h]
+\begin{figure}[h]
 \centering
-\includegraphics[width=\linewidth]{imgs/tpl_interface.png}
+\includegraphics[width=\columnwidth]{imgs/tpl_interface.png}
 \caption{TPL interface using Python script.
@@
 \label{fig:tpl_interface}
-\end{figure*}
+\end{figure}
 \subsection{Dashboard and forms}
@@
 The whole process is illustrated in figure \ref{fig:structure} (steps: 1, 2, 3, 8, 9).
-\begin{figure*}[ht]
-\centering
-\includegraphics[width=\linewidth]{imgs/allStructure.png}
-\caption{This figure shows the flow of data within the three tiers: (1) The actor interact with the presentation layer three ways: programming, viewing dashboards, or giving feedback; (2)The user interaction results in sending requests to the application layer to be processed; (3)The application layer starts processing inputs and relevant functions; (4) If there is any required data from the databases, a QUERY is sent to the data layer; (5) then, the data layer respond with the corresponding data from different databases (6,7); (8) The application layer then runs the required components using the distributed engines; (9) The output of step (7) is responded back to the presentation layer along with the logs/errors in JSON format.
-higher resolution image can be downloaded \href{https://user-images.githubusercontent.com/6969514/72152397-cee71700-33e5-11ea-9108-c6823d2be504.png}{here}
-}
-\label{fig:structure}
-\end{figure*}
 
@@
 BMS in different buildings are various, in terms of data structure, sampling rate, communication protocol, etc., making data querying a troublesome task.
-The platform dealt with this by deploying the PI system from OSIsoft \cite{PiSystem}, which queries data from different types of servers, such as BACnet (Building Automation and Control networks) and OPC (Open Platform Communications), and stores the compressed data on the local server.\par
-\begin{figure*}
-\includegraphics[width=\linewidth]{imgs/uml_relationship.jpeg}
-\caption{Relational database: A higher resolution image can be downloaded  \href{https://user-images.githubusercontent.com/6969514/72235771-e9e89f80-360e-11ea-9cf7-91c0f521576c.jpeg}{here}
+The platform dealt with this by deploying the PI system from OSIsoft, which queries data from different types of servers, such as BACnet (Building Automation and Control networks) and OPC (Open Platform Communications), and stores the compressed data on the local server.\par
+\begin{figure}
+\includegraphics[width=\columnwidth]{imgs/uml_relationship.jpeg}
+\caption{Relational database: A higher resolution image can be downloaded  \href{https://user-images.githubusercontent.com/6969514/72235771-e9e89f80-360e-11ea-9cf7-91c0f521576c.jpeg}{here}. 
 }
 \label{fig:relationDatabase}
-\end{figure*}
+\end{figure}
 Data exchange between the application layer and the data layer is done through RESTful API and mainly in JSON format.
@@
 The API will retrieve data from the server and send it back as a JSON file, which will then be plotted in the canvas.
-\section{Case study} \label{section:casestudy}
-In this section, we introduce a case-study to evaluate our platform.
+
+\section{Use case scenario} \label{section:casestudy}
+In this section, we introduce a use case based on Cockburn's template \cite{Cockburn1998UseTemplate}  to illustrate how the platform works.
+The use case is a parametric energy simulation of a small office building from ANSI/ASHRAE/IES Standard 90.1 commercial reference buildings \cite{Field2010UsingStudies} shown in figure \ref{fig:commrefbuild}.
+
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{paper_LateX/imgs/comm_ref_build.png}
+\caption{One of the reference buildings developed by the U.S.
+Department of Energy (DOE).
+The building represents a small office with 5,500 square feet area and one floor.
+The image is a screenshot taken from the embedded 3d viewer in our platform, and provided by BuildSimHub (in the application layer).
+an animated GIF of the 3d-viewer could be viewed \href{https://user-images.githubusercontent.com/6969514/77833696-3eb1a600-717a-11ea-8f77-475be6d57cfb.gif}{here}}
+\label{fig:commrefbuild}
+\end{figure}
+\textbf{USE CASE:1 Conduct a Parametric Energy Simulation}\\
+- - - - - - - - - - - - - - - - - - - - - - - - - - - \\
+CHARACTERISTIC INFORMATION\\
+\textbf{\underline{Context of use:}} EnergyModeller conducts a parametric building energy simulation of a small office building using the three-tier architecture platform.\\
+\textbf{\underline{Scope:}} Platform\\
+\textbf{\underline{Level:}} Summary\\
+\textbf{\underline{Preconditions:}} The user must have a valid authentication to the platform and a supported web browser (e.g. Google Chrome).\\
+\textbf{\underline{Actor(s):}} EnergyModeller, BuildSimHub (cloud simulation engine).\\
+\textbf{\underline{Trigger:}} Firstly, the EnergyModeller should start a new project. Secondly, IDF file of the EnergyPlus model of version greater than 8.0.
+
+\underline{Description: }
+\begin{enumerate}
+    \item EnergyModeller starts a new definition (project).
+    \item The IDF file link and global unique id (GUID) are retrieved. 
+    \item EnergyModeller uploads the IDF file to the data layer (a scalable google cloud bucket) using a file upload component (Figure \ref{fig:fileupload_comp}) -- an animated GIF image could be viewed \href{https://user-images.githubusercontent.com/6969514/77833649-16c24280-717a-11ea-9df1-8a5e0f7bae83.gif}{here}.
+
+    \item EnergyModeller loads a "buildSimHub Parametric Study" component (Figure \ref{fig:parametric_study}). 
+    \item fsdfsafasdf
+    \item fsdfsafasdf
+    \item fsdfsafasdf
+\end{enumerate}
+
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{paper_LateX/imgs/file_compo.png}
+\caption{ File upload component in the presentation layer: a) The user is prompted to select a file.
+The file is uploaded to a google cloud bucket; b) Then, the file could be triggered by its global unique id}
+\label{fig:fileupload_comp}
+\end{figure}
 
@@
 % This paper is a part of a project funded by the Ng Teng Fong Charitable Foundation (NTFCF) research funding.
-\clearpage
-\balance
+% \clearpage
+% \balance
 
@@
 
-\bibliography{references.bib,./references2.bib,SampleReferences.bib}
+\bibliography{references.bib,references2.bib}
 \end{document}

### 2020-03-30 paper_LateX/main.tex

@@
 This separation resulted in some advantages such as flexibility, scalability (horizontal and vertical), reusability, and latency reduction.
-\hl{Currently, the platform is in the final stage of development.
-The following stage includes community testing and user experience enhancement.}
+Currently, the platform is in the final stage of the alpha release development.
+The following stage includes community testing and user experience enhancement.
 \end{abstract}
@@
 
-\begin{figure*}[h]
+\begin{figure}[h]
 \centering
-\includegraphics[width=\linewidth]{imgs/platform_interface.png}
+\includegraphics[width=\columnwidth]{imgs/platform_interface.png}
 \caption{The main interface functions}
 \label{fig:platformInterface}
-\end{figure*}
+\end{figure}
 
@@
 
-\underline{Description: }
+\textbf{\underline{Description: }}
 \begin{enumerate}
-    \item EnergyModeller starts a new definition (project).
+    \item EnergyModeller starts a new definition -- (Tier1 - presentation layer).
+    \item In the presentation layer, the EnergyModeller uploads the IDF file to the data layer (Tier 3) which is a scalable google cloud bucket using a file upload component (Figure \ref{fig:fileupload_comp}).
+This step takes place through the application layer (Tier2) which contains a Google Cloud Storage application programming interface (API) and other file validation and security checks -- an animated GIF image could be viewed \href{https://user-images.githubusercontent.com/6969514/77833649-16c24280-717a-11ea-9df1-8a5e0f7bae83.gif}{here}.
     \item The IDF file link and global unique id (GUID) are retrieved. 
-    \item EnergyModeller uploads the IDF file to the data layer (a scalable google cloud bucket) using a file upload component (Figure \ref{fig:fileupload_comp}) -- an animated GIF image could be viewed \href{https://user-images.githubusercontent.com/6969514/77833649-16c24280-717a-11ea-9df1-8a5e0f7bae83.gif}{here}.
-
     \item EnergyModeller loads a "buildSimHub Parametric Study" component (Figure \ref{fig:parametric_study}). 
-    \item fsdfsafasdf
-    \item fsdfsafasdf
-    \item fsdfsafasdf
+    \item After running the component, a request is sent to the simulation engine in the application layer including the inputs (IDF file, project api key, and the simulation parameters). 
+    \item The output of the simulation comes in a form of JavaScript Object Notation (JSON) as well as a chart (Figure \ref{fig:plot_panel}) -- a full view of the project can be downloaded \href{https://user-images.githubusercontent.com/6969514/77868854-2ff8eb00-726f-11ea-837d-efedac7a80a5.png}{ here}.
 \end{enumerate}
@@
 \label{fig:fileupload_comp}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{paper_LateX/imgs/bsh_param.png}
+\caption{ Parametric simulation study: this component runs a cloud simulation engine in the application layer.
+The inputs are: (1) The project\_api\_key, i.e.
+a unique id for each simulation project, and is used to track the project and run different simulation models' progress; (2) file\_dir: which is the IDF file stored in the data layer (tier 3) in the form of a flat file; (3) The simulation parameters.
+After running the component, the outputs (4) come in the form of JavaScript Object Notation (JSON) object and a plot which can be displayed in a panel (Figure \ref{fig:plot_panel}) and embedded in a website.}
+\label{fig:parametric_study}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{paper_LateX/imgs/display_data_plot_json.png}
+\caption{ Display results as a chart and/or JSON tree in the presentation layer.}
+\label{fig:plot_panel}
 \end{figure}
@@
 
+\textbf{Currently, the platform still in the final stages of developing and debugging the alpha release.
+The platform will be released as an open source and contributions are welcome from the community.
+Contribution instructions will be available on the following GitHub repository}:
+
+\href{https://github.com/ideas-lab-nus/paper-SIMAUD2020-three-tier-architecture-platform}{https://github.com/ideas-lab-nus/paper-SIMAUD2020-three-tier-architecture-platform}
+
 Future development includes enabling real-time teamwork, version controls, besides continuous testing and user-experience improvements.
@@
 \section*{ACKNOWLEDGMENTS}
-% This paper is a part of a project funded by the Ng Teng Fong Charitable Foundation (NTFCF) research funding.
-% \clearpage
-% \balance
+This paper is a part of a project funded by the Ng Teng Fong Charitable Foundation (NTFCF) research funding.
+
+\balance
 

### 2020-03-30 paper_LateX/main.tex
Updates from Overleaf

@@
 \includegraphics[width=\columnwidth]{imgs/platform_interface.png}
-\caption{The main interface functions}
+\caption{The main interface functions -- a higher resolution image can be viewed \href{https://raw.githubusercontent.com/ideas-lab-nus/paper-SIMAUD2020-three-tier-architecture-platform/master/paper_LateX/imgs/platform_interface.png}{here.}}
 \label{fig:platformInterface}
@@
 \caption{TPL interface using Python script.
-The python script enables reading, writing inputs and outputs of different components, as well as adding pre/post processing functions to the inputs/outputs.}
+The python script enables reading, writing inputs and outputs of different components, as well as adding pre/post processing functions to the inputs/outputs -- a higher resolution image can be viewed \href{https://raw.githubusercontent.com/ideas-lab-nus/paper-SIMAUD2020-three-tier-architecture-platform/master/paper_LateX/imgs/tpl_interface.png}{here}}
 \label{fig:tpl_interface}
